\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning \versionline{4}

### 2015-09-03 ICRA2016/bandits_docs/includes/related_work.tex
First full version of the paper with committed adobe illustrator figures

\section{Related Work}

Many works on grasp planning focus on finding grasps by maximizing a grasp quality metric, such as the ability to resist external perturbations to the object in wrench space~\cite{ferrari1992, miller2004graspit}.
These metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{}.
However, analytic grasp quality metrics have been criticized for relying on perfect knowledge of object shape, pose, material properties, and locations of contact~\cite{cheong2011output} and the abliity of a gripper to actuate any contact force in the friction cone, which is not true of many real-world grippers~\cite{}.
Recent work has also suggested that grasp closure metrics may fail to accurately predict of grasp success on a physical robot~\cite{balasubmaranian, weisz}.
This has motivated work on transferring known grasps from a database to new objects, evaluating robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and work on data-driven grasp synthesis~\cite{}.

Many works have approached grasp synthesis for unknown or familiar objects by transferring grasps from a benchmark set of exemplar objects in a large database.
%Ciocarlie et al.~\cite{ciocarlie2009} found that human hand postures lie on a low-dimensional subspace, called eigen-grasps, and exploited this structure to speed up grasp optimization to synthesize grasps at a large scale in GraspIt!.
Li and Pollard~\cite{} generated grasps by matching object shapes to human hand postured in a database.
Hillebrand and Roa~\cite{} transfer grasps from objects of the same category using pose alignment and geometric warping betwen corresponding points on a shape surface.
Goldfelder et al.~\cite{} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 form closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{partial}.
Detry et al.~\cite{91inbohg} create a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{}.

Work on evaluating grasp quality metrics under uncertainty, such as the probability of force closure, has considered uncertainty in the state of a robotic gripper~\cite{goldberg1990bayesian, stulp2011learning} and uncertainty in contact locations with an object~\cite{zheng2005}.
Recent work has also studied the effects of uncertainty in object pose and gripper positioning~\cite{brook2011collaborative, hsiao2011bayesian}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} studied a Bayesian framework to evaluate the probability of grasp success given uncertainty in object identity, gripper positioning, and pose by simulating grasps on deterministic mesh and point cloud models.
Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} independently found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic wrench space metrics. 
Many works have also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{chris}, part tolerancing in manufacturing~\cite{kehoe}, or missing and noisy data from depth sensors such as the Kinect~\cite{mahler, laskey}.
Many have also studied caging gripper configurations, which may be a waypoint to form closure grasps and are robust to perturbations in object pose and shape~\cite{}.

Another approach for synthesizing grasps on objects is to sample grasps and rank them according to metrics derived from human labels or physical execution~\cite{bohg}.
Saxena et al.~\cite{bothsaxenaworks} used a logistic regression classified to predict grasp afordances in images from human annotated training data.
Several other works have examined predicting grasp points using depth gradient features~\cite{rao}, global shape context descriptors~\cite{}, and 3D edges~\cite{}. 
Lenz et al~\cite{lenz} used deep learning to detect grasp bounding boxes in color and depth images.
Herzog et al.~\cite{} extract "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Kappler et al.~\cite{} trained a deep neural network to predict human labelled grasps for a Barett hand on a database of synthetic objects.
Recently, several works have studied forming a database of grasps on synthetic objects from simulation outcomes~\cite{detry} or physical execution~\cite{tellex}.
In comparison, our work uses data-driven correlations between grasps based on local and global features of an object surface to quickly and adaptively acquire samples for evaluating and ranking grasps by their likelihood of success.

Active learning for grasp planning is an active area of research.
Several works have studied active search for successful grasps by minimzing uncertainty about the state of the envirnoment~\cite{kahn, vincsze}, but without use of an explicit grasp quality metric to guide the search.
Recently, Laskey et al.~\cite{} showed that MAB algorithms can be used to accelerate the identification of a grasp with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
Tellex et al.~\cite{} proposed an initiative to adaptively collect a dataset of grasps and point clouds for one million objects using MAB and reinforcemen learning.
MAB algorithms select the next grasp to sample by trading off gaining information about grasps with few samples and exploiting the success of grasps known to work well.
In robotics, MAB algorithms have also been for speeding up probabilistic roadmap motion planning by adaptively sampling waypoints~\cite{hsu2005hybrid}, searching for the best state machine for a particular task~\cite{matikainen2013multi}, solving mixed observable POMDPs~\cite{Mikko2015POMDP}, and multi-agent navigation~\cite{guy}.

One shortcoming of the MAB model used by Laskey et al. is that it did not take into account correlations between grasps~\cite{}.
In reality, grasp correlations may occure from grasps with similar poses~\cite{}, objects with similar global structure~\cite{}, or on surfaces with similar local geometry~\cite{}.
Correlated Multi-Armed Bandit (CMAB) models, also referred to as Bayesian Optimization models~\cite{}, have been used to trading off infromation gathering and exploitation in applicatoins such as ad-serving~\cite{}, next-best view prediction in object modeling~\cite{}, envrionmental monitoring in robotics~\cite{}.
Perhaps the most common model of correlations in a CMAB is a linear model~\cite{}, however this depends on the selection of features are linearly related to a success criteria.
Another common model of correlations is a Gaussian Process (GP)~\cite{}, which can model nonlinear relationships between options and rewards but are expensive to update with new observations ($O(n^2)$ where $n$ is the number of observations so far).
As a result, several fast approximate version of GP bandit algorithms exist, such as local GPs~\cite{} and hierarchical GPs~\cite{}.
Recently, Goetschalckx et al.~\cite{} developed the Continuous Correlated Beta Process (CCBP), a nonlinear model of 0-1 reward probabilities.
CCBPs are inexpensive to update compared to GPs, requiring $O(n)$ time in the worst case and a much smaller factor when efficient nearest neighbor queries can be performed~\cite{}.
In this work we utilize CCBPs to model correaltions between grasps because of their ability to scale to thousands of grasp observations with reasonable runtime.

>>>>

\section{Related Work}
\seclabel{related}

For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
Research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, miller2004graspit}, object WS~\cite{liu2015fast, pollard1994parallel}, or task WS~\cite{kruger2011partial, li1988task}.
WS metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{prattichizzo2008grasping}.
%This has motivated work on grasp transfer from a knowledge database to new objects, robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and synthesis from statistical models of grasping learned from physical data or human labels.

The need to recompute WS metrics to select grasps for every new object motivated research on grasp synthesis by transferring grasps from a database of exemplar objects.
Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
Recent research has also studied grasp transfer from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2014grasp, pokorny2013grasp}.

Another line of research focused on making analytic grasp metrics robust to imprecision in perception and control~\cite{goldberg1990bayesian, stulp2011learning, zheng2005}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} developed a Bayesian framework to evaluate both the expected epsilon quality and the probability of physical success on a PR2 given uncertainty in object identity, object pose, and gripper positioning on deterministic mesh and point cloud models. 
Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics. 
Kim et al.~\cite{kim2012physically} planned grasps using the expected epsilon quality metric~\cite{ferrari1992} under dynamics and uncertainty in pose, and found that the robust metric has a higher correlation with physical grasp success.
Recent research has also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward, panahi2015orienting}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{dragiev2013uncertainty, mahler2015gp, laskey2015bandits}.
%Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.

Recent research has also studied synthesizing grasps by ranking grasps according statistical models learned from human annotations or physical execution~\cite{bohg2014data}.
Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images, which was extended to real time by Redmon and Angelova~\cite{redmon2014real}.
Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.
Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict grasp success for a Barett hand measured by human annotations and the results of simulations on a database of synthetic pointclouds of objects.
Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
In comparison, we learn a model to predict a Bayesian distribution on the probability of force closure for a grasp on an object based on similarity to a set of prior grasps and objects in a database, and use our model to actively decide the next grasp to evaluate using Multi-Armed Bandits.

Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples.
Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Similarly, Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit (MAB) algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net with CCBPs to further reduce the number of samples needed to converge to a grasp with high quality.

### 2015-09-03 ICRA2016/bandits_docs/paper.tex
First full version of the paper with committed adobe illustrator figures

\begin{document}
\title{\LARGE \bf DexNet 1.0: Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{2}}
\author{Jeffrey Mahler, Brian Hou, Mel Roderick, Michael Laskey, Kai Kohlhoff, \\ Torsten Kroeger, Florian Pokorny, James Kuffner, Ken Goldberg}
%\institute{Deptartment of Electrial Engineering and Computer Sciences, University of California, Berkeley, USA
%\{jmahler, zmccarthy, sachinpatil, pabbeel, goldberg\}@berkeley.edu} 
\maketitle

\TODO{Possibly will include Matthieu Aubry and Pieter Abbeel as coauthors as well}

\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/background}
\input{includes/algorithm}
%\input{includes/analysis}
\input{includes/experiments}
%\input{includes/conclusion}

>>>>

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning
%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{4}}
\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Mel Roderick$^1$, Michael Laskey$^1$, Kai Kohlhoff$^3$, \\ Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{$^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
}
\maketitle

\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}

\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/background}
\input{includes/algorithm}
\input{includes/dataset}
\input{includes/experiments}
\input{includes/conclusion}
